---
title: "Assignment 4"
author: "Dan Weinberger"
date: "4/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(MASS)
source('./R/its_functions.R')
```

```{r}
# d1 <- read.csv('https://github.com/weinbergerlab/InterventionEvaluatR/raw/master/data-raw/PNAS/S1-Brazil.csv')
# d1 <- d1[d1$age_group==1, c('date','J12_18', 'ach_noj')]
# d1$date <- as.Date(d1$date)
# 
# d1 <- d1[order(d1$date),]
# saveRDS(d1, './Data/Brazil_hosp.rds')
```

```{r}
d1 <- readRDS('./Data/Brazil_hosp.rds')
```

Define vaccine introduction date

```{r}
vaccine_intro_date <- as.Date('2010-01-01')
```

Define when the evaluation period begins

```{r}
eval_date <- as.Date('2011-01-01')
```

Create some variables that might be helpful

```{r}

d1$time_index <- 1:nrow(d1)

#Indicator variables (0,1) for the different post-vaccine periods
d1$post1 <- 0
d1$post1[d1$date>=vaccine_intro_date] <- 1

d1$post2 <- 0
d1$post2[d1$date>=eval_date] <- 1

#Terms that can be used to construct a linear spline (connected line with changing slopes)
d1$spl1 <- 1:nrow(d1) - which(d1$date==vaccine_intro_date) + 1
d1$spl2 <- 1:nrow(d1) - which(d1$date==eval_date) + 1

d1$spl1[d1$spl1<0] <- 0
d1$spl2[d1$spl2<0] <- 0

d1$log_offset <- log(d1$ach_noj)
```

Fit a series of negative binomial regressions:
1) a trend +log(offset), 
2) a trend + step change +log(offset)
3) a trend + interaction between trend and step change variables +log(offset)
4) a trend + spline variables +log(offset)

```{r}

```


Now let's use a function that will allow us to get uncertainty intervals
```{r}
mod1 <- spline_func(time_points=d1$date,
                    ds=d1,
                    post_period1=c('2010-08-01', '2011-08-01'),
                    post_period2=c('2011-08-01', '2012-12-01'),
                    mod='negbin',
                    other.covars=c('time_index'),
                    denom='ach_noj',
                    outcome_name='J12_18',
                    vax.vars=c('post1','post2'))

mod1$rr.q.post

```

Plot your output
```{r, fig.width=8, fig.height=4}
plot.step.func(mod1)

```






